\documentclass[%draft,
    a4paper,
    11pt, % use explicit paper size
    headinclude, footexclude,
    notitlepage,
    headsepline,
    pointlessnumbers,
    ]{scrartcl}
\usepackage{pslatex} % -- times instead of computer modern

\typearea{14}
\usepackage{scrpage2} % for headers
 \setkomafont{pagehead}{\scshape\small}
 \setkomafont{pagenumber}{\scshape\small}
 \ihead[]{Martin Schoeberl}
 \ohead[]{Publications}

% \ofoot[]{} \cfoot[]{} \ifoot[]{}

\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{dcolumn}
\newcommand{\cc}[1]{\multicolumn{1}{c}{#1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\usepackage{boxedminipage}

\newcommand{\excelwidth}{\columnwidth}

\newcommand{\code}[1]{{\textsf{#1}}}


\begin{document}

\pagestyle{scrheadings}

\begin{center}
\vspace{3cm}
{\usekomafont{title}\huge Publications Martin Schoeberl}\\
\bigskip
\bigskip
\end{center}

I have published four books, 28 journal articles, one book chapter, one patent, and 165
papers in peer-reviewed conferences and workshops; 76 of the publications
as main author (39 of the 76 as single author).
Out of my top 10 cited papers, 5 papers are single-author papers, and on 4 papers
I am the first author.
According to Google Scholar (see \href{http://scholar.google.com/citations?user=wiRNmwUAAAAJ&hl=en&oi=ao}{Google profile}),
my papers are cited 4897 times, and my h index is 37.
My ORCID is  \href{https://orcid.org/0000-0003-2366-382X}{0000-0003-2366-382X}.

% The first article (JSA 2008) was the \textbf{most cited article at JSA} of articles published in the last five years.\footnote{\url{http://www.elsevier.com/wps/find/journaldescription.cws_home/505616/description}}

\subsection*{Five Most Important Publications}

\begin{itemize}

\item Martin Schoeberl, Sahar Abbaspour, Benny Akesson, Neil Audsley, Raffaele Capasso, Jamie Garside, Kees Goossens, Sven Goossens, Scott Hansen, Reinhold Heckmann, Stefan Hepp, Benedikt Huber, Alexander Jordan, Evangelia Kasapaki, Jens Knoop, Yonghui Li, Daniel Prokesch, Wolfgang Puffitsch, Peter Puschner, Andr\'{e} Rocha, Cl\'{a}udio Silva, Jens Spars{\o}, and Alessandro Tocchi.
 T-CREST: Time-predictable Multi-Core Architecture for Embedded Systems.
 \emph{Journal of Systems Architecture} 61(9):449--471, 2015.
 
 
This article summarizes the research and development work within the EC funded
project T-CREST. T-CREST is one of the few multi-core architectures where
WCET analysis of tasks executing on different cores is possible.
The article was written by researchers from all 9 partners of
the project. The paper is influential, as it has been already cited 189 times
within 6 years (according to Google Scholar).

\item Martin Schoeberl, Wolfgang Puffitsch, Rasmus~Ulslev
    Pedersen, and Benedikt Huber. Worst-case execution time
  analysis for a {Java} processor. {\em Software: Practice and
  Experience}, 40/6:507--542, 2010.
  
This article presents the worst-cases execution time (WCET) analysis tool for
the Java processor JOP.
The hardware design of JOP together with this tool is currently the only
solution for embedded Java where the worst-case execution time can
be predicted statically.

\item Christof Pitter and Martin Schoeberl.
A real-time {Java} chip-multiprocessor.
{\em ACM Trans. Embed. Comput. Syst.}, 10(1):9:1--34, 2010.

Together with my first PhD student Christof Pitter we built a time-predictable
chip-multiprocessor based on time-predictable memory arbitration and
several Java processors. To the best of my knowledge this was the first multicore
processor that was WCET analyzable and supported by a WCET analysis
tool.

\item Martin Schoeberl. Time-predictable computer architecture.
    {\em EURASIP Journal on Embedded Systems}, vol. 2009, Article
    ID 758480:17 pages, 2009.
    
This article take the basic ideas from the JOP design on time-predictable
computer architecture towards general purpose processors. This article was
the main article for my habilitation thesis, where I {\bf establish time-predictable
computer architecture as a research direction}.
Furthermore, the T-CREST project was based on the ideas presented in this article.


\item Martin Schoeberl. A Java processor architecture for
embedded real-time systems. {\em Journal of Systems
Architecture}, 54/1--2:265--286, 2008.

This article summarizes my PhD work on a time-predictable Java processor
(called JOP). This article was the \textbf{most cited article at JSA} of articles
published in the last five years for several years (it is now out of the 5 year
window.) Its citation count is 248.


   
%\item Martin Schoeberl. A time predictable instruction cache for
%    a {J}ava processor. In {\em On the Move to Meaningful
%    Internet Systems 2004: Workshop on {J}ava Technologies for
%  Real-Time and Embedded Systems (JTRES 2004)}, volume 3292 of
%  {\em LNCS}, pages 371--382, Agia Napa, Cyprus, October 2004.
%  Springer.
%
%This paper presents one of my first time-predictable features for a processor,
%the so called method cache, to simplify WCET analysis. This idea has been further
%explored by a whole PhD thesis by Stefan Metzlaff in Augsburg.




 
\end{itemize}

\subsection*{Books}

\begin{enumerate}

\item Martin Schoeberl. {\em Digital Design with Chisel}.
Number ISBN 9781689336031. Kindle Direct Publishing, August 2019. 

\item Martin Schoeberl. {\em JOP Reference Handbook: Building
    Embedded Systems with a Java Processor}. Number ISBN
978-1438239699. CreateSpace, August 2009.

\item Martin Schoeberl. {\em JOP: A Java Optimized Processor for
    Embedded Real-Time Systems}. Number ISBN 978-3-8364-8086-4.
    VDM Verlag Dr. M{\"u}ller, July 2008.

\item Doug Locke, B.~Scott Andersen, Ben Brosgol, Mike Fulton, Thomas Henties,
  James~J. Hunt, Johan~Olm\"{u}tz Nielsen, Kelvin Nilsen, Martin Schoeberl,
  Joyce Tokar, Jan Vitek, and Andy Wellings.
 Safety-critical {Java} technology specification, public draft, 2011.

\end{enumerate}

\subsection*{Book Chapter}

\begin{enumerate}

\item Martin Schoeberl.
 Hardware support for embedded {Java}.
 In M.~Teresa Higuera-Toledano and Andy~J. Wellings, editors, {\em
  Distributed, Embedded and Real-time {Java} Systems}, pages 159--176. Springer
  US, 2012.
\end{enumerate}

\subsection*{Patent}

\begin{enumerate}

\item Martin Schoeberl. Instruction Cache f\"ur Echtzeitsysteme,
    April 2006. Austrian patent AT 500.858.
\end{enumerate}


\subsection*{Theses}

\begin{enumerate}

\item Martin Schoeberl.
 Time-predictable computer architecture.
 Habilitation thesis, Institut for Computer Engineering, Vienna
  University of Technology, September 2009.

\item Martin Schoeberl. {\em JOP: A Java Optimized Processor for
    Embedded Real-Time Systems}. PhD thesis, Vienna University of
    Technology, 2005.
\end{enumerate}


\input{pub.tex}
  
\subsection*{Technical Reports}

\begin{enumerate}

\item Andrew Dobis, Tjark Petersen, Kasper Juul Hesse Rasmussen, Enrico Tolotto,
Hans Jakob Damsgaard, Simon Thye Andersen, Richard Lin, and Martin Schoeberl
  Open-source Verification with Chisel
  and Scala, available at \url{https://arxiv.org/abs/2102.13460}, 2021.

\item Jack Whitham and Martin Schoeberl.
 The limits of TDMA based memory access scheduling.
 Technical Report YCS-2011-470, University of York, 2011.

\item Martin Schoeberl, Benedikt Huber, Walter Binder, Wolfgang Puffitsch, and Alex
  Villazon.
 Object cache evaluation.
 Technical report, Technical University of Denmark, 2010.

\item Martin Schoeberl, Hiren D. Patel, and Edward A. Lee. Fun
    with a deadline instruction. Technical Report
UCB/EECS-2009-149, EECS Department, University of
  California, Berkeley, Oct 2009.
 

\end{enumerate}


\end{document}
